
```{r appendix-r-setup, results = "asis", echo = FALSE}
  ###   Set Table, Figure and Equation Counters
  #     - `prefix` is defined in the function `w_paper_paged`
  #     - manually define if available as YAML variable/meta-data
  if (!exists("prefix")) {
    #  e.g., "R" for "Appendix R" (or "A", "B", "R session", etc.)
    prefix <- rmarkdown::metadata$`appendix-prefix`
  }
  get.session.info <-
    !(exists("session_platform") & exists("attached_pkgs") & exists("namespace_pkgs"))
  cfaDocs::setCounters()
  options(table_counter = FALSE)
  options(table_num_str = paste0(prefix, "%d")) # Prepend Appendix Letter when using tblNum()
  options(table_counter_str = paste0("**Table ", prefix, "%s:**")) # "**Table R%s:**"
  options(fig_num_str = paste0(prefix, "%d")) # Prepend Appendix Letter when using figNum()
  options(fig_caption_no_sprintf = paste0("**Figure ", prefix, "%d:** %s")) # "**Figure R%d:** %s"
```

```{r r-session-info-r, echo = FALSE, eval = get.session.info}
  source("R_Session_Info.R")
```

# Computational Environment
Since `R` and `R` packages are constantly evolving, it is critical to document
information such as software package and library versions (primary and auxilary)
and the  computer system platform used in data analyses and report generation.
This appendix provides the `R` and system specifications used in the
`r ifelse(get.session.info, "creation of this report.", "analyses described in this report.")`

##  General `R` software and system information

```{r r-platform, echo = FALSE, eval = exists("session_platform")}
  knitr::knit_print(
    htmlTable::htmlTable(as.matrix(session_platform[, c(2,1)]), align = "rr",
      caption = cfaDocs::tblCap(("Platform Information for R Session"))))
```

<br/>

##  Attached and loaded `R` packages
The following (non-`base` `R`) packages were attached in the `R` session:

```{r r-session-packages, echo = FALSE, eval = exists("attached_pkgs")}
  knitr::knit_print(
    htmlTable::htmlTable(as.matrix(attached_pkgs), align = "rrrr",
      caption = cfaDocs::tblCap("Attached R Packages for R Session")))
```

<br/>

In addition to the attached packages in the table above, the following
packages were loaded via a namespace (and not attached):

```{r r-session-nmspc-pkgs, results = "asis", echo = FALSE, eval = exists("namespace_pkgs")}
  cat(
namespace_pkgs, sep = "\n\n")
```
