
```{r appendix-r-setup, results='asis', echo=FALSE}
  ###   Set Table, Figure and Equation Counters
  # the object `prefix` is defined in the function `w_paper_paged`
  cfaDocs::setCounters()
  options(table_counter=FALSE)
  options(table_num_str = paste0(prefix, "%d")) # Prepend Appendix Letter when using tblNum()
  options(table_counter_str = paste0("**Table ", prefix, "%s:**")) # "**Table A%s:**"
  options(fig_num_str = paste0(prefix, "%d")) # Prepend Appendix Letter when using figNum()
  options(fig_caption_no_sprintf = paste0("**Figure ", prefix, "%d:** %s")) # "**Figure A%d:** %s"
```

# Documenting the Computational Environment

Since `R` [@Rsoftware2022] and `R` packages are constantly evolving, it is critical to
document information such as software package versions (primary and auxilary) and the
computer system platform used during analyses and reporting [@Bauer2018-dl]. This appendix
provides the `R` and system specifications used in the analyses and creation of this report.

##  General `R` software and system information

```{r r-session-platform, echo=FALSE}
  r_session_info <- devtools::session_info()
  session_platform <- data.frame(unlist(r_session_info$platform))
  names(session_platform) <- "Value"
  session_platform$Setting <- rownames(session_platform)
  row.names(session_platform) <- NULL
  
  knitr::knit_print(
		htmlTable::htmlTable(as.matrix(session_platform[, c(2,1)]), align='rr',
	    caption = cfaDocs::tblCap(("Platform Information for R Session"))))
  ##  This might be needed for cfa_paged style appendix:
  # r-session-platform, fig.cap="R Session Platform Information", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}
	##  Include VERY small, transparent image to create table title and
	# knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)
```

<br/>

##  Attached and loaded `R` packages

The following packages (non-base `R`) were attached:


```{r r-session-packages, echo=FALSE}
  trim_source <- function(txt){
    split.at <- strsplit(txt, "@")[[1]]
    git.commit <- substr(split.at[2], 1, 7)
    if (!is.na(git.commit)) {
      paste0("    ", split.at[1], "@", git.commit, ")")
    } else txt
  }

  session_packages <- data.frame(r_session_info$packages, row.names = NULL)

  namespace_pkgs <- subset(session_packages, attached == FALSE, 
                           select = c(package, loadedversion))
  namespace_pkgs$alph <- toupper(unlist(lapply(namespace_pkgs$package, substr, 1, 1)))
  namespace_pkgs_alpha <- NULL
  for (n in unique(namespace_pkgs$alph)) {
    chnk <- subset(namespace_pkgs, alph == n)
    chnk <- paste0("**", chnk$package, "**", " *(", chnk$loadedversion, ")*")
    chnk <- paste(chnk, collapse = ", ")
    namespace_pkgs_alpha <- c(namespace_pkgs_alpha, chnk)
  }

  attached_pkg <- subset(session_packages, attached == TRUE, 
                         select = c(package, loadedversion, source, date))
  attached_pkg$source <- unlist(lapply(attached_pkg$source, trim_source))
  attached_pkg$date <- format(as.Date(attached_pkg$date), "%m/%d/%Y")
  names(attached_pkg) <- c("Package", "Version", "Source", "Date Installed")
  row.names(attached_pkg) <- NULL
  
  knitr::knit_print(
		htmlTable::htmlTable(as.matrix(attached_pkg), align='rrrr',
	    caption = cfaDocs::tblCap("Attached R Packages for R Session")))
```

<br/>

In addition to the attached packages in the table above, the following packages were loaded via a namespace (and not attached):

```{r r-session-nmspc-pkgs, results='asis', echo=FALSE}
  cat(
namespace_pkgs_alpha, sep = "\n\n")
```

<!--  End appendix format: re-start counters and change back to numeric for subsequent re-rendering-->

```{r r-session-reset, cache=FALSE, echo=FALSE}
	options(table_counter_str = NULL)
	options(table_num_str = NULL)
	options(fig_caption_no_sprintf = NULL)
	options(fig_num_str = NULL)
```

<!-- ## All the code in the paper

*** NOTE: This doesn't work when your using `child = ` in the "parent" .Rmd file!!! ***

To simply attach all the code you used in the PDF file in the appendix see the R
chunk in the underlying `.rmd` file:

```{r allrcode, ref.label=knitr::all_labels(echo == TRUE), echo=TRUE, eval=FALSE, results='asis'}
```
-->

<br/><br/>

# References {-}

::: {#refs_appndxR}
:::
