---
title: "Appendix R"
appendix-prefix: "R"
output:
  html_document:
    template: ../assets/pandoc/wp_appendix.html
    self_contained: true
---

<!--
  This document is intended to be rendered from the "Child_RMD" directory.
-->

# R Session Information

Since `R` [@Rsoftware2022] and `R` packages are constantly evolving, it is critical to
document information on the software version and packages that were loaded and system
platform used during analyses and reporting [@Bauer2018-dl]. This appendix provides the
`R` and system specifications used in the creation of do this report and its associated
analyses.

```{r r-session-info, echo=FALSE}
# set width option to force fit onto page margins
# options(width=75)
# print(sessionInfo(), locale = FALSE)
# when using child='Appendix_*.Rmd'
# knitr::knit_print(capture.output(print(sessionInfo(), locale = FALSE)))
pander::pander(sessionInfo(), compact = FALSE, locale=FALSE)

  #r-session-platform, fig.cap="R Session Platform Information", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}
	###  Include VERY small, transparent image to create table title and
	# knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)
  #
  # session_platform <- as.data.table(unlist(devtools::session_info()$platform), keep.rownames=T)[V1 != "tz"]
  # setnames(session_platform, c("Setting", "Value"))
  # row.names(session_platform) <- NULL
  #
  # knitr::knit_print(
	# 	htmlTable::htmlTable(as.matrix(session_platform), align='rr',
	#     caption = tblCap(knitr::opts_current$get("fig.cap"))))
```

<!--  End appendix format: re-start counters and change back to numeric for subsequent re-rendering-->

```{r, cache=FALSE, results='asis', echo=FALSE}
	options(table_counter_str = NULL)
	options(table_num_str = NULL)
	options(fig_caption_no_sprintf = NULL)
	options(fig_num_str = NULL)
```

<!-- ## All the code in the paper

*** NOTE: This doesn't work when your using `child = ` in the "parent" .Rmd file!!! ***

To simply attach all the code you used in the PDF file in the appendix see the R
chunk in the underlying `.rmd` file:

```{r, allrcode, ref.label=knitr::all_labels(echo == TRUE), echo=TRUE, eval=FALSE, results='asis'}
```
-->

<br><br><br>

# References {-}

::: {#refs_appndxR}
:::
